### 2018-04-17 paper/paper.tex
Update the answer 2.2.2.1

\paragraph
4
\paragraph
5
\end{document}

>>>>

\paragraph
4
\paragraph
5

\subsubsection{Adaptative gradient descent (GDad)}
\paragraph
1 The following plots demonstrate the results of Logistic Regression with iterations = 2000, learning rate $\eta$ = 1 and varying degrees $l$ = \{1, 2, 5, 15\}:
\begin{figure}[h]	
	\includegraphics[width=0.4	\textwidth]{logreg_deg1_iter20000.png}
	\includegraphics[width=0.4\textwidth]{logreg_deg1_iter20000_learn.png}
	\includegraphics[width=0.4\textwidth]{logreg_deg1_iter20000_error.png}
	\textbf{final learning rate : 3.25$e$\textsuperscript{-287}}
	\caption{degree $l$ = 1}
\end{figure}
\begin{figure}[h]	
\includegraphics[width=0.4	\textwidth]{logreg_deg2_iter2000.png}
\includegraphics[width=0.4\textwidth]{logreg_deg2_iter2000_learn.png}
\includegraphics[width=0.4\textwidth]{logreg_deg2_iter2000_error.png}
\textbf{final learning rate : 3.94$e$\textsuperscript{-274}}
\caption{degree $l$ = 2}
\end{figure}
\begin{figure}[h]	
\includegraphics[width=0.4\textwidth]{logreg_deg5_iter2000.png}
\includegraphics[width=0.4\textwidth]{logreg_deg5_iter2000_learn.png}
\includegraphics[width=0.4\textwidth]{logreg_deg5_iter2000_error.png}
\textbf{final learning rate : 15.3}
\caption{degree $l$ = 5}
\end{figure}
\begin{figure}[h]	
	\includegraphics[width=0.4\textwidth]{logreg_deg15_iter2000.png}
	\includegraphics[width=0.4\textwidth]{logreg_deg15_iter2000_learn.png}
	\includegraphics[width=0.4\textwidth]{logreg_deg15_iter2000_error.png}
	\textbf{final learning rate : 10.4}
	\caption{degree $l$ = 15}
\end{figure}

For each degree compare with the non-adaptive gradient descent variant. In particular, is the evolution of the learning rate numerically coherent with your previous guess of the optimal learning rate ? Discuss why GDad can be useful.

\end{document}
